%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[resmargin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[a4paper,margin=0.5in]{geometry}
%\documentclass[letterpaper,10pt]{article}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

%\usepackage[bottom=0.5in, top=0.

\usepackage{fancyhdr}
\setlength{\textwidth}{5.1in} % Text width of the document
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{amsmath}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.55in}
%\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-0.55in}
%\addtolength{\textheight}{1.0in}

% Sections formatting
\renewcommand\sectionfont{}%\bf\itshape

\usepackage{enumitem}
\usepackage[super]{nth}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,    % makes web links blue
    linkcolor=blue,   % makes internal links (like TOC) blue
    citecolor=blue    % makes citation links blue (if you use them)
}


\begin{document}


%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------


\hspace*{-\sectionwidth}\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{\Huge Mohamed Rayan Barhdadi\vspace{2pt}} &\hfill Doha, Qatar\\ % row = 1
  \href{https://www.linkedin.com/in/bmrayan/}{\uline{LinkedIn}} $|$
  \href{https://github.com/BMRayan/}{\uline{GitHub}} $|$
  \href{https://scholar.google.com/citations?user=G7qjc6kAAAAJ&hl=en&oi=ao}{\uline{Google Scholar}} $|$
  \href{https://bmrayan.github.io/}{\uline{Website}}  % row = 2 
   & 
   \texttt{rayan.barhdadi@tamu.edu} $|$ (+974) 5516-9477 \\ % row = 2
\end{tabular*}

\vspace{5pt} % Adjust vertical space before the line
\moveleft\hoffset\vbox{\hrule width 18.7cm height 0.5pt}\smallskip %... %----------------------------------------------------------------------------------------

\begin{resume}

%-----------------------------------------------------------------------------
%	RESEARCH INTEREST
%-----------------------------------------------------------------------------

\vspace{-20pt}
\section{Research Interests}

1. Physics-Informed Geometric Deep Learning Strategic Analysis \\
2. Foundation Multimodal AI for Scientific Applications


\vspace{-5pt}

%--------------------------------------------------------------------
%	EDUCATION
%--------------------------------------------------------------------

\section{Education}

{\bf Texas A\&M University}, Qatar Campus \hfill Aug 2023-Present \\
Bachelor of Science with Honors \hfill Graduation: May 2027 \\
Specialization: Electrical Engineering with minor in Mathematics and Physics \\
%GPA: overall 3.36/4.0; EE-only 3.63/4.0\\

\begin{itemize}[itemsep=0em]
\vspace{-10pt}
\item {\sl Thesis 1 (ongoing):} Toward Improving Physics-Guided 3D Reconstruction from Sparse Views.
\end{itemize}
%----------------------------------------------------------------------------------------
%	On-Going Work
%----------------------------------------------------------------------------------------
%\section{On-Going Work} 
%{\sl Novel diagnostic tool and API for transformer fault prediction using Machine Learning. \\
%Neural 3D Reconstruction from Minimal Data using Deep Learning}

\vspace{-6pt}
\section{Publications} 

{\bf M. R. Barhdadi}, H Kurban, and H Alnuweiri. {\sl PhysicsNeRF: Physics-Guided 3D Reconstruction from Sparse Views} . The 42$^{\text{nd}}$ International Conference on Machine Learning (ICML), Building Physically Plausible World Models, Vancouver, Canada 2025. {\sl[Accepted]}

\vspace{-4pt}
{\bf M. R. Barhdadi}, FF Jaldurgam, and SKE Awadallah. {\sl Advancing Transformer Diagnostics: A Statistical Analysis of a Publicly Available DGA Database} . The 21$^{\text{th}}$ CIGRE International Conference and 31$^{\text{st}}$ Exhibition for Electrical Equipment (GCC-CIGRE), Kuwait 2025. {\sl[Accepted]}

\vspace{-4pt}
{\bf M. R. Barhdadi}, and H Kurban. {\sl EMPATHIA: Multimodal Foundation Models for Culturally-Aware Human-AI Collaborative Integration of Displaced Populations} . The 39$^{\text{th}}$ Annual Conference on Neural Information Processing Systems (NeurIPS), San Diego CA, USA, 2025. {\sl[In Submission]}

\vspace{-4pt}
{\bf M. R. Barhdadi}, and H Kurban. {\sl Symbiotic Intelligence: Foundation Models for Human-Expert Collective Decision Making in Displacement Crisis Response} . The 39$^{\text{th}}$ Annual Conference on Neural Information Processing Systems (NeurIPS), San Diego CA, USA, 2025. {\sl[In Submission]} 

\vspace{-4pt}
{\bf M. R. Barhdadi}, and H Kurban. {\sl Dynamic PhysicsNeRFs: Foundation Models for 4D Reconstruction and Simulation} . The 11$^{\text{th}}$ IEEE MIT Undergraduate Research Technology Conference (MIT URTC), Boston MA, USA, 2025. {\sl[In Submission]}

\vspace{-4pt}
\M Aupetit, {\bf M. R. Barhdadi}, and H Bensmail {\sl Non-Volume Preserving Flow for Mode-Clustering of Multi-Dimensional Data}. Proceedings of 14$^{\text{th}}$ the International Conference on Learning Representations (ICLR ’26).


\vspace{-3pt}
%-------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{-3pt}
\section{Research \\ Experience}

{\bf Research Intern}, with Dr. Halima Bensmail \hfill May 2025-Present \\
Artificial Intelligence Group, Qatar Computing Research Institute 
\begin{itemize}[itemsep=0em]
\item Benchmarking state-of-the-art clustering algorithms including RealNVP and normalizing flows on high-dimensional biomedical datasets with automated parameter selection frameworks
\item Developing robust evaluation metrics and performance assessment protocols for unsupervised learning methods without manual hyperparameter tuning
\item Implementing deep generative models for complex data structure analysis, focusing on reproducibility and experimental design standards and preparing AAAI paper submission
\end{itemize} 
\vspace{-3pt}

{\bf Independent Lead Researcher} \hfill Mar 2025-Present \\
Supervised by Dr. Dr. Hasan Kurban and Dr. Hussein Alnuweiri
\begin{itemize}[itemsep=0em]
\item Led the development of PhysicsNeRF, a neural radiance field framework for 3D reconstruction from sparse views, integrating four physics-based constraints: monocular depth ranking, multi-view geometric consistency, volumetric sparsity priors, and progressive regularization.
\item Achieved state-of-the-art performance (21.4 dB average PSNR with only 8 input views) and analyzed generalization gaps and training dynamics, demonstrating how physics-guided constraints mitigate overfitting in under-constrained scenarios.
\item Authored and submitted a first-author paper on PhysicsNeRF to the ICML 2025 Building Physically Plausible World Models Workshop, providing theoretical and empirical insights into the limitations and potential of physics-informed deep learning for sparse 3D reconstruction.
\end{itemize}


\vspace{-3pt}
{\bf Research Collaborator}, Undergraduate Research Experience Program \hfill Jan 2025-Present \\
Qatar Research, Development and Innovation Council 
\begin{itemize}[itemsep=0em]
\item Developing machine learning frameworks for time-series analysis of industrial sensor data using advanced statistical methods and anomaly detection algorithms
\item Building predictive models with historical pattern recognition and implementing scalable data analytics pipelines for real-time processing
\item Designing robust APIs for automated data processing workflows and fault prediction systems with enhanced reliability metrics
\end{itemize} 

\vspace{-3pt}
{\bf Undergraduate Research Assistant}, with Dr. Selma Awadallah \hfill Feb 2024-Dec 2024 \\
Power System Modeling and Analysis Laboratory, Electrical and Computer Engineering Department, Texas A\&M University 

\begin{itemize}[itemsep=0em]
\item Designed and managed specialized MySQL database systems for large-scale monitoring data from 1,000+ transformers with over 18,200 samples, implementing comprehensive data quality control procedures
\item Performed multivariate statistical analysis and advanced data visualization techniques on dissolved gas analysis patterns, developing automated clustering and classification algorithms
\item Developed Python and SQL scripts for automated data extraction, processing, and visualization workflows, creating reproducible analysis pipelines for industrial monitoring applications
\end{itemize}

\vspace{-5pt}
\section{Teaching \\ Experience}
{\bf Mentor}, High School Research Experience Program \hfill Feb 2024-Dec 2024 \\
Qatar Research, Development and Innovation Council in collaboration with Texas A\&M University  \\
Environmental Data Collection and Analysis Project
\begin{itemize}[itemsep=0em]
\item Supervised long-term environmental data collection protocols using HOBO loggers and multi-parameter environmental sensor for temperature, wind patterns, and solar radiation over 10-month periods
\item Coordinated systematic data acquisition campaigns and implemented quality assurance procedures for environmental monitoring research with statistical validation methods
\end{itemize}

\vspace{-5pt}
\section{Industry \\ Experience}

{\bf SLB Qatar Headquarter} \hfill June 2025--July 2025 \\
Engineering/Data Science Intern
\begin{itemize}[itemsep=0em]
\item Developed a TL plugin/script to automate standardized cement and corrosion evaluation reports, integrating user-defined intervals, cement quality snapshots, and corrosion zonation studies (plots, tables) directly in Techlog, addressing a key bottleneck in well integrity reporting.
\item Reduced report turnaround time from 2-3 days to a few minutes, driving internal efficiency gains across 8 GeoUnits and enabling potential external revenue of $\sim\$100$k; facilitated bundling of auto-generated reports with acquisition deliverables for enhanced client value.
\end{itemize}


%----------------------------------------------------------------------------------------
%	OTHER EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-5pt}
\section{Other \\ Experience} 

Qatar Foundation - Student Housing, {\sl Front Desk Assistant} \hfill Nov 2024-Present \\
TAMUQ - Marketing and Communications Department, {\sl Student Assistant} \hfill Oct 2024-Present\\
Izu Studio - Motion Design Agency, {\sl Founder \& Motion Designer} \hfill June 2020-Aug 2024

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\vspace{-5pt}
\section{Awards}
2025 Travel Award to ICML - Dept. ECEN, Texas A\&M University Qatar -- \$1,500. \\
2025 Undergraduate Research Scholars - College of Engineering, Texas A\&M University. \\
2025 Second Place (Global Phase) Invent for the Planet by Texas A\&M University -- \$2,500. \\
2025 First Place at the EC 3rd Annual Undergraduate Research Retreat -- \$550. \\
2025 Woqod x Qatar Foundation Grant Award Recipient -- \$10,000. \\
2025 First Place (Qatar Phase) Invent for the Planet by Texas A\&M University Engineering -- \$1,650. \\
2025 Best Prototype Award Invent for the Planet by Texas A\&M University Engineering. \\
2025 Best Video Award Invent for the Planet by Texas A\&M University Engineering. \\
2025 Awardee of Student Leadership Exchange Program (SLEP) Grant -- \$2,000. \\
2024 Winner of Qatar Foundation Technology-Based Ideas Pitch Competition -- \$11,000 investment.\\
2024 Awardee of the selective Undergraduate Research Experience Program (UREP 31-043-2-014) by Qatar Research Development and Innovation Council (QRDI) -- \$1,500.\\
2024 2nd Place Texas A\&M University Qatar Robotics Competition.\\
2024 Lead Organizer and Mentor in "Effective Humanitarian Engineering Solutions Workshop".\\
2023 Inducted in Engineering Honors Program at Texas A\&M-Q. 

%----------------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------------
\vspace{-5pt}
\section{Technical Skills}

{\bf Programming Languages, Tools, Frameworks, Concepts:}  \\
\begin{itemize}[itemsep=0em]
\vspace{-5pt}
\item {\bf Programming Languages:} Python, Julia, SQL, C Language, Verilog HDL, HTML, CSS.
\item {\bf Machine Learning and Data Analysis Libraries:} PyTorch, TensorFlow, CUDA, scikit-learn, Pandas, NumPy, Matplotlib, Seaborn, SciPy, SymPy.
\item {\bf Software Tools and IDEs:} Intel Quartus II, Jupyter Notebook, VS Code, MobaXterm, MySQL Workbench, phpMyAdmin, XAMPP, HOBOlink.
\item {\bf Design and Media Tools:} Blender, LaTeX, Adobe Suite (After Effects, Media Encoder, Photoshop, Illustrator), Microsoft Office Suite (Excel, Word, PowerPoint).
\end{itemize}

%----------------------------------------------------------------------------------------
%	Leadership and Community Involvement
%----------------------------------------------------------------------------------------
\vspace{-3pt}
\section{Leadership and Community Involvement} 

The Peace Club TAMU-Q, {\sl President} \hfill Spring 2025 \\
The Peace Club TAMU-Q, {\sl Vice-President} \hfill Fall 2024 \\
Qatar Foundation, {\sl Student Orientation Leader} \hfill Fall 2024 \\
Qatar Foundation Convocation 24', {\sl Student Volunteer} \hfill Spring 2024 \\
IEEE, {\sl Student Member} \hfill Fall 2023-Present \\
IEEE Student Chapter, {\sl Class Representative} \hfill Fall 2023-Spring 2024 \\
Moroccan National Swimming Federation, {\sl Instructor Volunteer} \hfill Summer 2022

%----------------------------------------------------------------------------------------
%	Posters
%----------------------------------------------------------------------------------------
\vspace{-3pt}

\section{Posters } 

{\bf M. R. Barhdadi}, advised by Dr. Hussein Alnuweiri. {\sl Neural 3D Reconstruction from Minimal Data using Deep Learning} [Poster]. Winner/Best Poster (1$^{\text{st}}$ Place), Hamad Bin Khalifa University - Texas A\&M Qatar 3$^{\text{rd}}$ Annual Undergraduate Research Retreat, 2025.

\vspace{-4pt}

{\bf M. R. Barhdadi}, advised by Dr. Selma Awadallah. {\sl Transformer Monitoring: A Comprehensive Multidimensional Database for Dissolved Gas Analysis} [Poster]. Presented at the Hamad Bin Khalifa University STEAM Showcase, 2024.

%----------------------------------------------------------------------------------------
%	Presentations
%----------------------------------------------------------------------------------------

\vspace{-3pt}
\section{Presentations \\ and Talks} 

{\sl OmniWave 1.0: Technical Deployment of a Near-Shore Wave Energy Converter for Coastal Electrification} [Co-presented]. Winner (1$^{\text{st}}$ Place), Invent for the Planet Competition, Texas A\&M University Engineering (IFTP '25).

\vspace{-4pt}

{\sl Developing an AI-Powered Multisport Coaching Marketplace} [Co-presented]. Winner, Qatar Foundation Technology-Based Ideas Pitch Competition, HiEd Entrepreneurship \& Innovation Summit, 2024 (HiEd '24).

%----------------------------------------------------------------------------------------
%	Language Proficiency
%----------------------------------------------------------------------------------------
\vspace{-3pt}
\section{Languages}

English (Fluent), French (Fluent), Arabic (Native) 

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------
\vspace{-3pt}
\section{References}

{\bf Dr. Hasan Kurban} \\
Assistant Professor of CS at Hamad Bin Khalifa University, {\bf Email:} hkurban@hbku.edu.qa.

\vspace{-6pt}
{\bf Dr. Halima Bensmail} \\
Principal Scientist at the Qatar Computing Research Institute, {\bf Email:} hbensmail@hbku.edu.qa.

\vspace{-6pt}
{\bf Dr. Hussein Alnuweiri} \\
Professor of EE at Texas A\&M University Qatar, {\bf Email:} alnuweiri@tamu.edu.

\vspace{-6pt}
{\bf Dr. Ali Ghrayeb} \\
IEEE Fellow and Professor of EE at Texas A\&M University Qatar, {\bf Email:} ali.ghrayeb@qatar.tamu.edu.

\vspace{-6pt}
{\bf Dr. Selma Awadallah} \\
Assistant Professor of EE at Texas A\&M University Qatar, {\bf Email:} selma.awadallah@tamu.edu.


%\vspace{6pt}
%\noindent\hfill \textit{Last modified: Jan 2025}

\end{resume}
\end{document}
